---
title: "Assignment 1 test"
author: "Mia Keane"
date: "2024/01/12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require('tidyverse')
``` 

## R Markdown

I've added text here to show that I can write in an R document 
Here are some of my favorite things

- cats
- books
- camping


When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r mpg}
summary(mpg)
```

## Average mpg

You can also embed plots, for example:

```{r avgmpg}
avgmpgdata <- mpg %>% 
  group_by(manufacturer) %>% 
  summarize(hwy = mean(hwy), cty = mean(cty))

g <- ggplot(data = avgmpgdata)
g + geom_col(aes(x = cty, y = reorder(manufacturer, cty), fill = manufacturer)) +
  ggtitle("Average Miles per Gallon for City Driving by Manufacturer", subtitle = "Data on vehicles from 1999 to 2008 for 38 popular models of cars") +
  theme(legend.position="none") 
```